Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-29 prop_letter.tex
prop_letter.tex \section{Gleason} Start reconstruction...

While the finite-precision extension of the Kochen-Specker theorem
asserts the non-existence of a certain kind of QIVPMs, we also want
to understand what a QIVPM could be when it exists. A conventional
quantum probability measure~$\mu$ can easily be constructed using
the Born rule when one knows the current state of the system~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.
Gleason's theorem asserts that the only state consistent with $\mu$
on all projectors is the one used to construct $\mu$ by the Born
rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}. In
other words, the set of all quantum probability measures corresponds
one-to-one to the set of states, so that studying the set of states
is sufficient to understand all possible phenomena regarding to quantum
probability. Although we can extend the Born rule to its finite precision
version easily, there are some subtleties to extending Gleason's theorem.
If we only focus on the Born QIVPMs~$\bar{\mu}$, that is, QIVPM's
induced by a state~$\rho$ according to the Born rule, we find that
if we monotonically shrink the length of intervals, the states consistent
with $\bar{\mu}$ will be closer and closer to $\rho$, and vice versa.
However, there is a QIVPM such that no state can be consistent with
it on every projector. In another words, although the Born rule and
Gleason's theorem can be extended to consider finite precision measurement,
the problem of finite precision measurement itself is not limited
to error analysis in experimental results, but it highlights some
new phenomena regarding the foundation of quantum mechanics, and it
is necessary to embed the idea of the resources available for realistic
measurement into the formulation of quantum theory.

@@

>>>>

\begin{comment}
While the finite-precision extension of the Kochen-Specker theorem
asserts the non-existence of a certain kind of QIVPMs, we also want
to understand what a QIVPM could be when it exists. A conventional
quantum probability measure~$\mu$ can easily be constructed using
the Born rule when one knows the current state of the system~\citep{Born1983,peres1995quantum,544199,Jaeger2007}.
Gleason's theorem asserts that the only state consistent with $\mu$
on all projectors is the one used to construct $\mu$ by the Born
rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}. In
other words, the set of all quantum probability measures corresponds
one-to-one to the set of states, so that studying the set of states
is sufficient to understand all possible phenomena regarding to quantum
probability. Although we can extend the Born rule to its finite precision
version easily, there are some subtleties to extending Gleason's theorem.
If we only focus on the Born QIVPMs~$\bar{\mu}$, that is, QIVPM's
induced by a state~$\rho$ according to the Born rule, we find that
if we monotonically shrink the length of intervals, the states consistent
with $\bar{\mu}$ will be closer and closer to $\rho$, and vice versa.
However, there is a QIVPM such that no state can be consistent with
it on every projector. In another words, although the Born rule and
Gleason's theorem can be extended to consider finite precision measurement,
the problem of finite precision measurement itself is not limited
to error analysis in experimental results, but it highlights some
new phenomena regarding the foundation of quantum mechanics, and it
is necessary to embed the idea of the resources available for realistic
measurement into the formulation of quantum theory.
\end{comment}

@@

\yutsung{Compare the norm we used with other distances. For example,
the trace distance defined in Sec.~9.2.1 in Nielsen and Chuang~\citep{544199}.}
